\documentclass[10pt, letterpaper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% Formatting
\geometry{left=0.75in, right=0.75in, top=0.6in, bottom=0.6in}
\pagestyle{empty}
\raggedright

% Colors
\definecolor{primary}{RGB}{0, 70, 140} % Professional Blue

% Sections
\titleformat{\section}{
  \large\bfseries\color{primary}\uppercase
}{}{0em}{}[\titlerule]

\titlespacing{\section}{0pt}{12pt}{6pt}

% Custom Commands
\newcommand{\entry}[4]{
  \textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \textit{#4}
}

\begin{document}

% Header
\begin{center}
    {\Huge\textbf{Harsh Shah}} \\ \vspace{4pt}
    harshmkvviv@gmail.com | +1-5164341033 \\
    \href{https://linkedin.com/in/harsh-h-shah}{LinkedIn} | \href{https://github.com/harsh-h-shah}{GitHub} | \href{https://www.harsh.software}{Portfolio}
\end{center}

\vspace{6pt}

% Education
\section{Education}

\entry{Stony Brook University}{New York, USA}{Master of Science}{2024-08 -- 2026-05}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=15pt]
    \item Relevant Coursework: Algorithms, Operating Systems, Wireless Networks, Data Structures
\end{itemize}
\vspace{4pt}

\entry{University of Mumbai – Thadomal Shahani Engineering College}{Mumbai, India}{Bachelor of Engineering}{2020-08 -- 2024-05}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=15pt]
    \item Relevant Coursework: Databases, Computer Networks, Web Systems
\end{itemize}
\vspace{4pt}


% Experience
\section{Experience}

\entry{Meta \& Major League Hacking}{Remote}{Production Engineering Fellow}{2025-06 -- 2025-09}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=15pt]
    
    \item Selected for a competitive 12-week, course-based Production Engineering fellowship with mentorship from industry-experts.
    
    \item Built internal dashboards and monitoring UIs using React.js and Chart.js, improving observability for containerized systems.
    
    \item Built and deployed backend infrastructure using Docker, Linux, and Nginx for scalable analytics platforms.
    
    \item Designed system telemetry pipelines using Prometheus \& Grafana, improving observability \& reliability.
    
\end{itemize}
\vspace{6pt}

\entry{Aumsat Technologies}{Mumbai, India}{Software Developer Intern}{2023-06 -- 2023-10}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=15pt]
    
    \item Built a ground subsidence detection system processing 500+ geospatial datasets, enabling data-driven urban planning decisions.
    
    \item Consumed Python/Flask APIs and integrated map-based visualizations using Leaflet.js and custom UI widgets.
    
    \item Performed backend automation \& data pipeline optimization in Python, reducing processing times by 40\%.
    
\end{itemize}
\vspace{6pt}


% Projects
\section{Projects}

\textbf{ZapMap Electric Vehicle Charging Station Locator} \hfill \href{https://github.com/Harsh-H-Shah/ZapMap}{Link} \\
\textit{Flutter, Flask, Docker}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=15pt]
    
    \item Designed an EV charging platform with microservices, REST APIs, serving 100+ stations at 98\% uptime.
    
    \item Engineered a custom A* pathfinding algorithm, cutting route calculation time by 60\% vs. Dijkstra’s algorithm.
    
    \item Integrated 3+ APIs (TomTom, eDRV, Stripe) for navigation, charger status, and secure payments with 99.9\% availability.
    
\end{itemize}
\vspace{4pt}

\textbf{Rashi Pay - Offline Payment Interface} \hfill \href{}{Link} \\
\textit{React Native, TailwindCSS, Express.js}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=15pt]
    
    \item Built an offline digital payment app using Bluetooth, enabling 40\% faster P2P transfers without internet.
    
    \item Winner of Smart India Hackathon 2022 among 400 teams, delivering a cross-platform solution with React Native + Express.js.
    
    \item Secured 10,000+ test transactions via 2048-bit RSA encryption, ensuring safe and reliable P2P payments.
    
\end{itemize}
\vspace{4pt}

\textbf{Alpha Trading} \hfill \href{https://github.com/Harsh-H-Shah/Alpha-trading}{Link} \\
\textit{React.js, Firebase, TailwindCSS}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=15pt]
    
    \item Developed a real-time paper trading platform with live updates for 500+ NSE stocks.
    
    \item Achieved 85\% prediction accuracy using an LSTM model for 30-day stock forecasting.
    
    \item Optimized platform performance with efficient state management and real-time data streaming.
    
\end{itemize}
\vspace{4pt}


% Skills
\section{Technical Skills}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=15pt]
    
    
    \item \textbf{ Programming Languages:} Python, Java, C++, JavaScript, TypeScript
    
    
    
    \item \textbf{ Frontend Development:} React.js, Next.js, Angular (basics), component-driven UI
    
    
    
    \item \textbf{ Backend Development:} REST, GraphQL, gRPC, microservices, object-oriented design
    
    
    
    \item \textbf{ Databases:} PostgreSQL, MySQL, MongoDB, Redis
    
    
    
    \item \textbf{ Cloud Platforms:} AWS, Azure, GCP, Cisco Cloud
    
    
\end{itemize}

% Achievements

\section{Achievements}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=15pt]
    
    \item \textbf{ Winner at HopperHacks 2025 \& HackNYU 2025 } (2025) -- Best Overall Project \& Best Use of Streamlit among 235+ projects.
    
    \item \textbf{ Ranked top 20 at Harbinger 2.0 RBI International hackathon } (2023) -- Out of 363 teams from 22 countries for scalable blockchains.
    
    \item \textbf{ Winner at Smart India Hackathon 2022 } (2022) -- Among 30,000 teams nationwide for developing an offline payments interface.
    
\end{itemize}


% Publications

\section{Publications}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=15pt]
    
    \item ``A Cloud-Based Architecture for EV Charge Station Finder with Efficient Scheduling'', \textit{ CSA 2024 Conference } (2024).
    
\end{itemize}


\end{document}